Automating Verification of MPC Security: $\metaprot$ to $\minifed$

### 2024-04-19 revision-1/lang.tex
checkpoint

\subsubsection{Library Functions}

@@

Given a variable-free boolean expression $\be$, we write $\cod{\be}$
to denote the standard interpretation of $\be$ in the arithmetic field
$\mathbb{Z}{p}$.
With the introduction of variables to expressions, we need to interpret
variables with respect to a specific memory, and all
variables used in an expression must belong to a specified client.  Thus,
we denote interpretation of expressions $\be$ possibly containing
variables as $\lcod{\store,\be}{\cid}$, where $\store$ associates
variables with values, and all variables must be owned by client
$\cid$. This is interpretation is defined in Figure \ref{fig-minifed}.

$$
\delta(\otp,v_1,v_2) \defeq v_1 \fplus v_2
$$

>>>>

\subsubsection{Library Functions} $\minifed$ expression syntax also supports
calls to library functions $f$. This allows encapsulation and separate
definition of primitive operations such as one-time-pads and message
authentication, as we will illustrate with examples. This approach is
useful since it parameterizes these definitions, and 
supports verification of behavior specified with types, as we
discuss in Section \ref{section-types}.

@@

Given a variable-free expression $\be$, we write $\cod{\be}$ to denote
the standard interpretation of $\be$ in the arithmetic field
$\mathbb{Z}_{p}$. With the introduction of variables to expressions,
we need to interpret variables with respect to a specific memory, and
all variables used in an expression must belong to a specified client.
Thus, we denote interpretation of expressions $\be$ computed on a
client $\cid$ as $\lcod{\store,\be}{\cid}$. This interpretation is
defined in Figure \ref{fig-minifed}. It is also parameterized by
$\delta$ which defines the semantics of library functions $f$.

The small-step reduction relation $\redx$ is then defined in Figure
\ref{fig-minifed} to evaluate commands. Reduction is a relation on
\emph{configurations} $(\store, \prog)$ where all three command forms-
message send, broadcast, and output- are implemented as updates to the
memory $\store$. We write $\redxs$ to denote the reflexive, transitive
closure of\ $\redx$.

\subsection{Example: Passive-Secure Addition}

Shamir addition leverages homomorphic properties of addition in
arithmetic fields to implement secret addition. If a field value $v_1$
is in a uniform random distribution with other variables in a program,
then $v_1 \fplus v_2$ is an encryption of $v_2$ where $v_1$ is an
information theoretically secure one-time-pad, which is exploited for
secret sharing. Of course, $\fplus$ is also a meaningful operation
over any two field values regardless of their distributions.

To capture this distinction we introduce a function $\otp$
with the following specification:
$$
\delta(\otp,v_1,v_2) \defeq v_1 \fplus v_2
$$
Although the semantics are the same as addition, the use of $\otp$
makes a declarative distinction, but more importantly we will be
able to assign a type to $\otp$ that enforces the one-time discipline
on its first argument via type linearity as will be discussed in Section
\ref{section-types}.
